The future of the NBA is on the Horizon

### 2024-04-21 paper/paper.qmd
Paper update

library(tidyverse)
library(knitr)
library(modelsummary)
library(tinytex)
library(lubridate)
library(viridis)
library(gt)
library(arrow)
```

@@

## Results 1

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-nbastats
#| fig-cap: NBA Statistics from 1980

@@

### resulstss

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-newnbastats
#| fig-cap: NBA Stats Since 2004

@@

# Discussion

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-scoringgraph
#| fig-cap: High Scoring games(59+ pts)

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-scoringgraph1980
#| fig-cap: High Scoring games(59+ pts) Since 1980

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-scoringgraph70
#| fig-cap: High Scoring games(70+ pts) Since 1980

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-lebronbar
#| fig-cap: Lebrons PPG as a Ratio of the League Average

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-lebronarea
#| fig-cap: League Average PPG vs Lebrons PPG

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig-cap: Linear NBA Model

>>>>

library(tidyverse)
library(knitr)
library(modelsummary)
library(tinytex)
library(lubridate)
library(viridis)
library(gt)
```

@@

## Results 1
rr
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-nbastats
#| fig-cap: NBA Statistics from 1980
#| fig-pos: 'H'

@@

### resulstss
rrr
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-newnbastats
#| fig-cap: NBA Stats Since 2004
#| fig-pos: 'H'

@@

# Discussion
rrrrr
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-scoringgraph
#| fig-cap: High Scoring games(59+ pts)
#| fig-pos: 'H'

@@

rrrrr

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-scoringgraph1980
#| fig-cap: High Scoring games(59+ pts) Since 1980
#| fig-pos: 'H'

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-scoringgraph70
#| fig-cap: High Scoring games(70+ pts) Since 1980
#| fig-pos: 'H'

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-lebronbar
#| fig-cap: Lebrons PPG as a Ratio of the League Average
#| fig-pos: 'H'

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-lebronarea
#| fig-cap: League Average PPG vs Lebrons PPG
#| fig-pos: 'H'

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig-cap: Linear NBA Model
#| fig-pos: 'H'
